Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-10 grove-paper.tex
Fix spacing after vertex and edge names (Michael D. Adams)

For example, in \autoref{fig:Move} Alice continues her edits by
moving \texttt{\hole{} * y} from the left child of \texttt{+} to its right child.
This corresponds to the following sequence of graph edits, shown in \autoref{fig:Move}:
(a) delete \eWrapPlus leaving \vSimpleTimes temporarily orphaned and 
(b) add \eMoveTimes to \vSimpleTimes in the right child position of \vWrapPlus.

>>>>

For example, in \autoref{fig:Move} Alice continues her edits by
moving \texttt{\hole{} * y} from the left child of \texttt{+} to its right child.
This corresponds to the following sequence of graph edits, shown in \autoref{fig:Move}:
(a) delete \eWrapPlus{} leaving \vSimpleTimes{} temporarily orphaned and 
(b) add \eMoveTimes{} to \vSimpleTimes{} in the right child position of \vWrapPlus{}.
